\begin{thebibliography}{99999}
\phantomsection
\singlespace\normalsize

%\addtocontents{toc}{\protect\newpage}

\bibitem{data_mining_image} The Hadoop architecture image extracted from \url{http://blog.raremile.com/hadoop-demystified/} accessed on May 2015.

\bibitem{rest_client_ruby} A ruby library used for executing REST requests over HTTP. \url{https://github.com/rest-client/rest-client} accessed on May 2015.

\bibitem{d3} JavaScript library D3 for constructing data-driven documents \url{http://d3js.org/} accessed on May 2015.

\bibitem{uaic} POS tool provided by Universitatea "Alexandru Ioan Cuza" din Iași under SOAP service \url{http://nlptools.infoiasi.ro/WebPosRo/PosTaggerRoWS?wsdl} accessed on May 2015.

\bibitem{racai} POS tool provided by Institutul de Cercetări pentru Inteligență Artificială "Mihai Drăgănescu", Academia Română under SOAP service \url{http://ws.racai.ro/ttlws.wsdl} accessed on May 2015.

\bibitem{nokogiri_gem} A ruby library used for XML parsing \url{https://github.com/sparklemotion/nokogiri} accessed on May 2015.

\bibitem{mongoid_gem} A ruby ORM for MongoDB \url{http://mongoid.org/en/mongoid/index.html} accessed on May 2015.

\bibitem{savon_gem} A ruby library used for SOAP communication \url{http://savonrb.com/} accessed on May 2015.

\bibitem{mongo_to_postgres} An business story of migrating the project from MongoDB to PostgreSQL \url{http://developer.olery.com/blog/goodbye-mongodb-hello-postgresql/} accessed on May 2015.

\bibitem{mongodb} MongoDB official page \url{https://www.mongodb.org/} accessed on May 2015

\bibitem{wiki_data_mining} The official page of Wikipedia on topic of data mining \url{http://en.wikipedia.org/wiki/Data_mining} accessed on May 2015



\bibitem{wiki_data_journalism} The official page of Wikipedia on topic of data journalism \url{http://en.wikipedia.org/wiki/Data_journalism}

\bibitem{wiki_column_based_db} The official page of Wikipedia on topic of Column Based Database Management Systems \url{http://en.wikipedia.org/wiki/Column-oriented_DBMS} accessed on May 2015



\end{thebibliography}
