\begin{thebibliography}{99999}
\phantomsection
\singlespace\normalsize

\bibitem{wiki_data_mining} The official page of Wikipedia on topic of data mining \url{http://en.wikipedia.org/wiki/Data_mining} accessed on May 2015

\bibitem{Ak} Akins R.E. Performance evaluation of wind-energy conversion systems using the method of bins - current status. Internal.Report SAND-77-1375. Sandia Laboratory, USA, 1978. 

\bibitem{And}Anderson J.D., Fundamentals of aerodynamics, 2nd Edition. McGraw-Hill, Singapore.

\bibitem{booch} Booch G. et. al\textit{., }Object-Oriented Analysis and Design with
Applications, Addison-Wesley 2007.

\bibitem{Bostan}
Bostan I., Dulgheru V., Sobor I., Bostan V., Sochirean A., Sisteme de
conversie a energiilor regenerabile, Technica-Info 2007.

\bibitem{Xfoil}Drela M. Xfoil : An Analysis and Design System for Low Reynolds Number Airfoils. Low Reynolds Number Aerodynamics, Springer-Verlag, Lec. Notes in Eng. 54, 1989.

\bibitem{gamma} Gamma E., Helm R., Johnson R., Vlissides J.\textit{, }Design Patterns -
Elements of Reusable Object-Oriented Software, Addison-Wesley 1994.

\bibitem{Larman1} Larman C., Agile and Iterative Development: A Manager's Guide, Adisson
Wessley 2003.

\bibitem{Larman2} Larman C., Applying UML and Patterns: An Introduction to Object-Oriented
Analysis and Design and the Unified Process, Addison Wessley 2002.

\bibitem{PITAC} President’s Information Technology Advisory Committee, Computational Science: Ensuring America’s Competitiveness, Report to President, \url{http://www.nitrd.gov/pitac/reports/20050609_computational/computational.pdf}, June 2005. 

\bibitem{CwithUML} \url{http://www.drdobbs.com/184401948}

\bibitem{Pic1}Super-sized 6.15MW Wind Turbine Up and Running, 2050 Magazine, \url{http://www.2050publications.com/super-sized-6-15mw-wind-turbine-up-and-running/}

\bibitem{Pic2}Largest Wind Farm in Europe Alive, \url{http://www.renewindians.com/2012/12/Largest-Wind-Farm-in-Europe.html}

\bibitem{Pic3}GE Power \& Water, Renewable energy, \url{http://www.ge-renewable-energy.com/uploads/tx_spdownloads/Fantanele_Romania_2.xWEA_03.JPG}



\end{thebibliography}
